---
title: "Master Thesis - Statistical Analysis"
author: "Marlene Rüschoff"
date: "2026-01-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/marlenerueschoff/Documents/Uni/UzK Master/Masterarbeit/Experiment/masterthesis_experiment-1/Data/V6")
```


# Setup

```{r cars}
# Load libraries
library(tidyverse)
library(janitor)
library(dplyr)
library(skimr)
library(naniar)
library(tidyr)
library(ggplot2)
library(stringr)
library(GGally)
library(effectsize)
library(e1071)    
library(car)      
library(lmtest)   
library(sandwich) 
library(purrr)
library(broom)
library(patchwork)
```

# Data Loading

```{r}
# Primary Data
demographics   <- read.csv("demographics.csv")  
mouse_events   <- read.csv("mouse_events_norm.csv")
mouse_hovers   <- read.csv("mouse_hovers.csv")  
participants   <- read.csv("participants.csv")  
questionnaires <- read.csv("questionnaires.csv") 
velocity_metrics <- read.csv("velocity_metrics_norm.csv")
submovement_metrics <- read.csv("submovement_metrics_norm.csv")
hover_metrics  <- read.csv("hover_metrics.csv")

# Explorative Data
direction_changes <- read.csv("direction_changes.csv")
pause_analysis <- read.csv("pause_analysis.csv")
velocity_by_phase <- read.csv("velocity_by_phase.csv")
```


# Data Preparation

## Calculation of Scale Scores (Questionnaires)

### PAAS

```{r}
# Rename column
questionnaires <- questionnaires %>%
  rename(PAAS_Score = paas)
```


### NRQ

```{r}
# Calculate Means of Scores (ICL, ECL, Total)
questionnaires <- questionnaires %>%
  mutate(
    NRQ_ICL_Score = rowMeans(select(., NRQ_ICL1, NRQ_ICL2), na.rm = TRUE),
    NRQ_ECL_Score = rowMeans(select(., NRQ_ECL1, NRQ_ECL2, NRQ_ECL3), na.rm = TRUE),
    NRQ_Score = rowMeans(select(., NRQ_ICL1, NRQ_ICL2, NRQ_ECL1, NRQ_ECL2, NRQ_ECL3), na.rm = TRUE)
  )
```

### PIES

```{r}
# Calculate PIES Score
# item 2 and 3 are reverse-scored
questionnaires <- questionnaires %>%
  mutate(
    # reverse scoring (1–7): new = 8 - old
    PIES2_rev = 8 - PIES2,
    PIES3_rev = 8 - PIES3,

    # overall product interest score = average of 11 items
    PIES_Score = rowMeans(
      cbind(PIES1, PIES2_rev, PIES3_rev, PIES4, PIES5, PIES6, PIES7, PIES8, PIES9, PIES10, PIES11),
      na.rm = TRUE))


```

### ECM

```{r}
# Calculate ECM Score
questionnaires <- questionnaires %>%
  mutate(
    # CI is reverse-scored
    ECM_CI3_rev = 8 - ECM_CI3
  ) %>%
  rowwise() %>% 
  mutate(
    # subscale scores (CI, S, PU)
    ECM_CI_Score = mean(c_across(c(ECM_CI1, ECM_CI2, ECM_CI3_rev)), na.rm = TRUE),
    ECM_S_Score  = mean(c_across(c(ECM_S1, ECM_S2, ECM_S3, ECM_S4)), na.rm = TRUE),
    ECM_PU_Score = mean(c_across(c(ECM_PU1, ECM_PU2, ECM_PU3, ECM_PU4)), na.rm = TRUE),
    ECM_Score    = mean(c_across(c(
      ECM_CI1, ECM_CI2, ECM_CI3_rev,
      ECM_S1, ECM_S2, ECM_S3, ECM_S4,
      ECM_PU1, ECM_PU2, ECM_PU3, ECM_PU4
    )), na.rm = TRUE)
  ) %>%
  ungroup()

```

### Attention Check
```{r}
# filter the rows where the attention check was answered wrong
questionnaires <- questionnaires %>%
  filter(PIES_AC == "5" | PIES_AC == "1")
```



## Merge Data (df)

```{r}
# Merge all data into df
df =  demographics %>%
  left_join(participants, by = "participant_id") %>%
  left_join(questionnaires,   by = "participant_id") %>%
  left_join(hover_metrics, by = "participant_id") %>%
  left_join(submovement_metrics, by = "participant_id") %>%
  left_join(velocity_metrics, by = "participant_id") %>%
  left_join(direction_changes %>% select(participant_id, n_direction_changes, dir_changes_per_s), by = "participant_id")


# Remove unimportant columns
df <- df %>%
  select(-t1_detergent, -t1_smartwatch, -t1_speaker, -t1_bottle, -t1_toothbrush, -t1_backpack, -NRQ_ECL1, -NRQ_ECL2, -NRQ_ECL3, 
         -PIES1, -PIES2, -PIES3, -PIES2_rev, -PIES3_rev, -PIES4, -PIES5, -PIES6, -PIES7, -PIES8, -PIES9, -PIES10, -PIES11, -ECM_PU1, -ECM_PU2, -ECM_PU3, -ECM_PU4, -ECM_S1, -ECM_S2, -ECM_S3, -ECM_S4, -ECM_CI1, -ECM_CI2, -ECM_CI3, -ECM_CI3_rev, -NRQ_ECL1, -NRQ_ECL2, -NRQ_ECL3, -NRQ_ICL1, -NRQ_ICL2, -updated_at.x,-updated_at.y)
```


## Data Cleaning

a. Remove NAs
```{r}
# Remove rows with NAs
ids_to_drop <- bind_rows(
  df   %>% filter(if_any(everything(), is.na)) %>% distinct(participant_id)) %>%
  distinct(participant_id)

df   <- df   %>% 
  anti_join(ids_to_drop, by = "participant_id")

# Check 
#df[ rowSums(is.na(df)) > 0, ]
```

b. Adjust labels
```{r}
# Adjustment of employment labels
df <- df %>%
  mutate(
    employment = str_squish(employment),  # entfernt doppelte Spaces
    employment = case_when(
      employment %in% c("Selbstständig", "Self employed", "Self-employed") ~ "Self-employed",
      employment == "Student"                                              ~ "Unemployed",
      TRUE ~ employment
    )
  )
```

c. Set factor variables
```{r}
# Set factor variables
df <- df %>% 
  mutate(gender = factor(gender),
         employment = factor(employment),
         condition = factor(condition),
         interest = relevel(factor(interest), ref = "Low"),
         load = relevel(factor(load),ref = "Low"))
```


d. Save
```{r}
# Save df
#write.csv(df, "df.csv", row.names = FALSE)
```


e. Prepare supplementary dataframes

```{r}
# Pause analysis: merge conditions from df and set factors
pause_analysis <- pause_analysis %>%
  inner_join(
    df %>% select(participant_id, events_per_s, gender),
    by = "participant_id") %>%
  mutate(
    interest = factor(interest, levels = c("Low", "High")),
    load     = factor(load, levels = c("Low", "High"))
  )
```

```{r}
# Velocity by phase: merge conditions from df and set factors
velocity_by_phase <- velocity_by_phase %>%
  inner_join(
    df %>% select(participant_id, interest, load, trial_duration_s, events_per_s),
    by = "participant_id"
  ) %>%
  mutate(
    interest = factor(interest, levels = c("Low", "High")),
    phase    = factor(phase, levels = c("early", "mid", "late"))
  )
```


# Descriptive Analysis

```{r}
# Overview of variable types
str(df)
```

```{r}
# Summary statistics
summary(df)
```

## Descriptive Statistics

### Condition Distribution

```{r}
df %>%
  filter(!is.na(condition) & condition != "") %>%
  count(condition, name = "n") %>%
  mutate(prop = n / sum(n))
```

### Mouse Metrics

```{r}
# Mouse Metrics

## Variables
dvs <- c(
  "mean_velocity_norm_s",
  "total_distance_norm",
  "submovements",
  "mean_submovement_deviation",
  "mean_hovertime_s"
)

## Compute mean, SD, Median, IQR, Min and Max
summary_metrics_fun <- function(data, var) {
  data %>%
    summarise(
      N      = sum(!is.na(.data[[var]])),
      Mean   = mean(.data[[var]], na.rm = TRUE),
      SD     = sd(.data[[var]], na.rm = TRUE),
      Median = median(.data[[var]], na.rm = TRUE),
      IQR    = IQR(.data[[var]], na.rm = TRUE),
      Min    = min(.data[[var]], na.rm = TRUE),
      Max    = max(.data[[var]], na.rm = TRUE),
      .groups = "drop"
    )
}

## Summary metrics by interest 
summary_metrics_interest <- map_dfr(dvs, \(v) {
  df %>%
    group_by(interest) %>%
    summary_metrics_fun(v) %>%
    mutate(variable = v, .before = 1)
})

summary_metrics_interest

## Summary metrics by interest x load 
summary_metrics <- map_dfr(dvs, \(v) {
  df %>%
    group_by(interest, load) %>%
    summary_metrics_fun(v) %>%
    mutate(variable = v, .before = 1)
})

summary_metrics
```

```{r}
# Mean values by condition
df %>%
  group_by(condition) %>%
  summarise(
    n = n(),
    mean_velocity = mean(mean_velocity_norm_s, na.rm = TRUE),
    mean_total_distance = mean(total_distance_norm, na.rm = TRUE),
    mean_total_hovertime_s = mean(total_hovertime_s, na.rm = TRUE),
    mean_n_hovers = mean(n_hovers, na.rm = TRUE),
    mean_submovements = mean(submovements, na.rm = TRUE),
    mean_submovment_deviation = mean(mean_submovement_deviation, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
# Mean values by cognitive load
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_velocity = mean(mean_velocity_norm_s, na.rm = TRUE),
    mean_total_distance = mean(total_distance_norm, na.rm = TRUE),
    mean_total_hovertime_s = mean(total_hovertime_s, na.rm = TRUE),
    mean_submovements = mean(submovements, na.rm = TRUE),
    mean_submovment_deviation = mean(mean_submovement_deviation, na.rm = TRUE),
    .groups = "drop"
  )
```

### Questionnaire Scores

```{r}
# Summary Statistic for Cognitive Load Measurements (PAAS + NRQ)
summary_stats_load <- df %>%
  group_by(load) %>%
  summarise(
    PAAS_mean = mean(PAAS_Score, na.rm = TRUE),
    PAAS_sd = sd(PAAS_Score, na.rm = TRUE),
    PAAS_max = max(PAAS_Score, na.rm = TRUE),
    PAAS_min = min(PAAS_Score, na.rm = TRUE),
    NRQ_ICL_mean = mean(NRQ_ICL_Score, na.rm = TRUE),
    NRQ_ICL_sd = sd(NRQ_ICL_Score, na.rm = TRUE),
    NRQ_ICL_max = max(NRQ_ICL_Score, na.rm = TRUE),
    NRQ_ICL_min = min(NRQ_ICL_Score, na.rm = TRUE),
    NRQ_ECL_mean = mean(NRQ_ECL_Score, na.rm = TRUE),
    NRQ_ECL_sd = sd(NRQ_ECL_Score, na.rm = TRUE),
    NRQ_ECL_max = max(NRQ_ECL_Score, na.rm = TRUE),
    NRQ_ECL_min = min(NRQ_ECL_Score, na.rm = TRUE),
    NRQ_mean = mean(NRQ_Score, na.rm = TRUE),
    NRQ_sd = sd(NRQ_Score, na.rm = TRUE),
    NRQ_max = max(NRQ_Score, na.rm = TRUE),
    NRQ_min = min(NRQ_Score, na.rm = TRUE),
  )

# Summary Statistic for Interest Measurements (PIES + ECM)
summary_stats_interest <- df %>%
  group_by(interest) %>%
  summarise(
    PIES_mean = mean(PIES_Score, na.rm = TRUE),
    PIES_sd = sd(PIES_Score, na.rm = TRUE),
    PIES_max = max(PIES_Score, na.rm = TRUE),
    PIES_min = min(PIES_Score, na.rm = TRUE),
    ECM_mean = mean(ECM_Score, na.rm = TRUE),
    ECM_sd = sd(ECM_Score, na.rm = TRUE),
    ECM_max = max(ECM_Score, na.rm = TRUE),
    ECM_min = min(ECM_Score, na.rm = TRUE),
  )

# Print summary statistics
print(summary_stats_load)
print(summary_stats_interest)
```

### Demographics

a. Gender 
```{r}
gender_dist <- df %>%
  filter(!is.na(gender) & gender != "") %>%
  count(gender, name = "n") %>%
  mutate(prop = n / sum(n)) %>%
  arrange(desc(n))

gender_dist

ggplot(gender_dist, aes(x = reorder(gender, n), y = n, fill = gender)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, y = "Count", title = "Gender Distribution") 

```

b. Age

```{r}
ggplot(df, aes(x = age, fill = "Age")) +
  geom_histogram(bins = 20) +
  labs(x = "Age", y = "Count", title = "Age Distribution") +
  guides(fill = "none")


age_table <- df %>%
  mutate(
    age_group = cut(
      age,
      breaks = c(18, 25, 35, 45, 55, 65, Inf),
      right = FALSE,                 # right not included
      labels = c("18–24", "25–34", "35–44", "45–54", "55–64", "65+")
    )
  ) %>%
  filter(!is.na(age_group)) %>%     
  count(age_group, name = "N") %>%
  mutate(
    percent = 100 * N / sum(N)
  )

age_table


```

c. Employment

```{r}
employment_dist <- df %>%
  filter(!is.na(employment) & employment != "") %>%
  count(employment, name = "n") %>%
  mutate(prop = n / sum(n))
employment_dist

ggplot(employment_dist, aes(x = reorder(employment, n), y = n, fill = employment)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, y = "Count", title = "Employment distribution")

```

d. Education

```{r}
# Education distribution
education_dist <- df %>%
  filter(!is.na(education) & education != "") %>%
  count(education, name = "n") %>%
  mutate(prop = n / sum(n))

education_dist

# Plot
ggplot(education_dist, aes(x = reorder(education, n), y = n, fill = education)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(x = NULL, y = "Count", title = "Education distribution")

```



# Exploratory Data Analysis

## Box Plots: Mouse Metrics 

### Velocity

```{r}
# Summary interest x velocity 
df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    mean_velocity = mean(mean_velocity_norm_s, na.rm = TRUE)
  )

# Summary load x velocity
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_velocity = mean(mean_velocity_norm_s, na.rm = TRUE)
  )

# Plot: Velocity by interest
ggplot(df, aes(x = interest, y = mean_velocity_norm_s)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.12, alpha = 0.3) +
  labs(x = "Interest", y = "Mean velocity (norm/s)")

# Plot: Velocity by interest and load
ggplot(df, aes(x = interest, y = mean_velocity_norm_s, fill = load)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75), alpha = 0.6) +
  geom_jitter(aes(color = load),
              position = position_jitterdodge(jitter.width = 0.12, dodge.width = 0.75),
              alpha = 0.3) +
  labs(x = "Interest", y = "Mean velocity (norm/s)", fill = "Load", color = "Load")

```

### Total Distance

```{r}
# Summary interest x distance 
df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    mean_total_distance = mean(total_distance_norm, na.rm = TRUE)
  )

# Summary load x distance
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_total_distance = mean(total_distance_norm, na.rm = TRUE)
  )

# Plot: Distance by interest
ggplot(df, aes(x = interest, y = total_distance_norm)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.12, alpha = 0.3) +
  labs(x = "Interest", y = "Total distance (norm)")

# Plot: Distance by interest and load
ggplot(df, aes(x = interest, y = total_distance_norm, fill = load)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75), alpha = 0.6) +
  geom_jitter(aes(color = load),
              position = position_jitterdodge(jitter.width = 0.12, dodge.width = 0.75),
              alpha = 0.3) +
  coord_cartesian(ylim = c(0, 150)) +   # <- max auf 5 setzen (anpassen)
  labs(x = "Interest", y = "Total distance (norm)", fill = "Load", color = "Load")

```
### Submovements

```{r}
# Summary interest x submovements
df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    mean_submovements = mean(submovements, na.rm = TRUE),
    .groups = "drop"
  )

# Summary load x submovements
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_submovements = mean(submovements, na.rm = TRUE),
    .groups = "drop"
  )

# Plot: Submovements by interest
ggplot(df, aes(x = interest, y = submovements)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.12, alpha = 0.3) +
  labs(x = "Interest", y = "Number of submovements")

# Plot: Submovements by interest and load
ggplot(df, aes(x = interest, y = submovements, fill = load)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75), alpha = 0.6) +
  geom_jitter(aes(color = load),
              position = position_jitterdodge(jitter.width = 0.12, dodge.width = 0.75),
              alpha = 0.3) +
  labs(x = "Interest", y = "Number of submovements", fill = "Load", color = "Load")


```
### Submovement Deviation 

```{r}
# Summary interest x deviation
df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    mean_submovment_deviation = mean(mean_submovement_deviation, na.rm = TRUE),
    .groups = "drop"
  )

# Summary load x deviation
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_submovment_deviation = mean(mean_submovement_deviation, na.rm = TRUE),
    .groups = "drop"
  )

# Plot: Deviation by interest
ggplot(df, aes(x = interest, y = mean_submovement_deviation)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.12, alpha = 0.3) +
  labs(x = "Interest", y = "Submovement Deviation")

# Plot: Deviation by interest and load
ggplot(df, aes(x = interest, y = mean_submovement_deviation, fill = load)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75), alpha = 0.6) +
  geom_jitter(aes(color = load),
              position = position_jitterdodge(jitter.width = 0.12, dodge.width = 0.75),
              alpha = 0.3) +
  labs(x = "Interest", y = "Submovement Deviation", fill = "Load", color = "Load")

```

### Hover Time

```{r}
# Summary interest x hover time
df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    mean_total_hovertime_s = mean(total_hovertime_s, na.rm = TRUE),
    .groups = "drop"
  )

# Summary load x hover time
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_total_hovertime_s = mean(total_hovertime_s, na.rm = TRUE),
    .groups = "drop"
  )

# Plot: Hover time by interest
ggplot(df, aes(x = interest, y = total_hovertime_s)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.12, alpha = 0.3) +
  labs(x = "Interest", y = "Mean hover time (s)")

# Plot: Hover time by interest and load
ggplot(df, aes(x = interest, y = total_hovertime_s, fill = load)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75), alpha = 0.6) +
  geom_jitter(aes(color = load),
              position = position_jitterdodge(jitter.width = 0.12, dodge.width = 0.75),
              alpha = 0.3) +
  coord_cartesian(ylim = c(0, 250)) +  
  labs(x = "Interest", y = "Mean hover time (s)", fill = "Load", color = "Load")

```



### All Metrics (by Interest)

```{r}
# Mouse Metrics
mouse_vars <- c(
  "mean_velocity_norm_s",
  "total_distance_norm",
  "submovements",
  "mean_submovement_deviation",
  "total_hovertime_s"
)

# Box Plots
p <- df %>%
  pivot_longer(all_of(mouse_vars), names_to = "metric", values_to = "value") %>%
  ggplot(aes(interest, value)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.25) +
  facet_wrap(~metric, scales = "free_y", ncol = 5) +
  labs(x = NULL, y = NULL)
p

# Save
#ggsave("mouse_metrics.png", p, width = 16, height = 4, units = "in", dpi = 300)

```

## Distributions and Correlations 

```{r}
# Extract Mouse metrics as numerical variables
df_num <- df %>%
  select(all_of(mouse_vars)) %>%
  mutate(across(everything(), as.numeric)) %>%
  na.omit()

# GGPairs
GGally::ggpairs(
  df_num,
  upper = list(continuous = wrap("cor", size = 3)),
  diag  = list(continuous = "densityDiag"),
  lower = list(continuous = wrap("points", alpha = 0.35, size = 0.8))
)

```


##  Skewness 

```{r}
# Inspect skewness and decide on log transform

# Variables to check
vars_to_check <- c(
  "mean_velocity_norm_s",
  "mean_submovement_deviation",
  "submovements",
  "total_distance_norm",
  "total_hovertime_s",
  "trial_duration_s",
  "n_events",
  "events_per_s"
)

# Inspect distribution
inspect_var <- function(y, name = "y") {
  y_num <- suppressWarnings(as.numeric(y))
  y_num <- y_num[is.finite(y_num)]

  cat("\n====", name, "====\n")
  cat("n =", length(y_num), "\n")
  cat("min/median/mean/max =",
      signif(min(y_num),4), "/",
      signif(median(y_num),4), "/",
      signif(mean(y_num),4), "/",
      signif(max(y_num),4), "\n")
  cat("skewness =", signif(e1071::skewness(y_num, na.rm = TRUE, type = 2), 4), "\n")
  cat("share <= 0 =", signif(mean(y_num <= 0), 4), "\n")

  # Histogram
  print(
    ggplot(data.frame(y = y_num), aes(x = y)) +
      geom_histogram(bins = 40) +
      labs(title = paste0("Histogram (raw): ", name), x = name, y = "Count")
  )

  # Histogram (log) or (log1p)
  if (length(y_num) == 0) return(invisible(NULL))

  if (all(y_num > 0)) {
    print(
      ggplot(data.frame(logy = log(y_num)), aes(x = logy)) +
        geom_histogram(bins = 40) +
        labs(title = paste0("Histogram (log): ", name),
             x = paste0("log(", name, ")"), y = "Count")
    )
  } else if (all(y_num >= 0)) {
    print(
      ggplot(data.frame(log1py = log1p(y_num)), aes(x = log1py)) +
        geom_histogram(bins = 40) +
        labs(title = paste0("Histogram (log1p): ", name),
             x = paste0("log1p(", name, ")"), y = "Count")
    )
  } else {
    cat("Note: negative values present (log not applicable).\n")
  }
}

# Run inspection for all variables
for (v in vars_to_check) {
  if (!v %in% names(df)) {
    cat("\n[SKIP] Variable not found in df:", v, "\n")
    next
  }
  inspect_var(df[[v]], v)
}

# Model diagnostics for all five outcomes: RAW vs LOG/LOG1P
# Predictors
x_formula <- "interest"  

diag_plots <- function(m, title_prefix = "") {
  par(mfrow = c(1, 2))
  plot(m, which = 1, main = paste0(title_prefix, "Residuals vs Fitted"))
  plot(m, which = 2, main = paste0(title_prefix, "Normal Q-Q"))
  par(mfrow = c(1, 1))
  cat("\nBreusch-Pagan test (heteroskedasticity):\n")
  print(lmtest::bptest(m))
}

for (y_name in vars_to_check) {
  if (!y_name %in% names(df)) next

  y <- df[[y_name]]
  y <- suppressWarnings(as.numeric(y))
  y <- y[is.finite(y)]

  cat("\n=============================\nOutcome:", y_name, "\n=============================\n")

  f_raw <- as.formula(paste0(y_name, " ~ ", x_formula))
  m_raw <- lm(f_raw, data = df)
  cat("\n--- Diagnostics: RAW ---\n")
  diag_plots(m_raw, paste0("RAW (", y_name, "): "))

  # Decide log vs log1p vs skip
  if (all(df[[y_name]] > 0, na.rm = TRUE)) {
    f_log <- as.formula(paste0("log(", y_name, ") ~ ", x_formula))
    m_log <- lm(f_log, data = df)
    cat("\n--- Diagnostics: LOG ---\n")
    diag_plots(m_log, paste0("LOG (", y_name, "): "))
    cat("\nAIC comparison:\n")
    print(AIC(m_raw, m_log))

  } else if (all(df[[y_name]] >= 0, na.rm = TRUE)) {
    f_log1p <- as.formula(paste0("log1p(", y_name, ") ~ ", x_formula))
    m_log1p <- lm(f_log1p, data = df)
    cat("\n--- Diagnostics: LOG1P ---\n")
    diag_plots(m_log1p, paste0("LOG1P (", y_name, "): "))
    cat("\nAIC comparison:\n")
    print(AIC(m_raw, m_log1p))

  } else {
    cat("\n[INFO] Contains negative values (skipping log diagnostics).\n")
  }
}


```

-> mean velocity is slightly right skewed (skewness = 1.752) and log-transformation seems reasonable (see plot) 
-> mean submovement deviation is strongly right skewed (skewness = 2.674) and log-transformation seems reasonable (see plot) 
-> number of submovements are right skewed (skewness = 2.716) and log-transformation seems reasonable (see plot) 
-> total distance is right skewed (skewness = 3.453) and log-transformation seems reasonable (see plot) 
-> total hovertime is strongly right skewed (skewness = 6.303) and log-transformation seems reasonable (see plot)
-> trial_duration_s  is strongly right skewed (skewness = 6.142) and log-transformation seems reasonable (see plot)
-> n_events is strongly right skewed (skewness = 5.901) and log-transformation seems reasonable (see plot)
-> events_per_s is left skewed (skewness = -2.327) but log-transformation does not really help





# Questionnaires

## Reliability Check - Cronbach's Alpha

```{r}
############# NRQ ##############
# select the relevant NRQ items
NRQ_ECL_items <- questionnaires %>%
  dplyr::select("NRQ_ECL1","NRQ_ECL2","NRQ_ECL3")

NRQ_ICL_items <- questionnaires %>%
  dplyr::select("NRQ_ICL1", "NRQ_ICL2" )

# compute Cronbach's alpha
NRQ_ECL_alpha <- psych::alpha(NRQ_ECL_items)
NRQ_ICL_alpha <- psych::alpha(NRQ_ICL_items)

############# PIES ##############
# select the relevant PIES items
PIES_items <- questionnaires %>%
  dplyr::select("PIES1", "PIES2_rev", "PIES3_rev", "PIES4", "PIES5", "PIES6", "PIES7", "PIES8", "PIES9", "PIES10", "PIES11")

# compute Cronbach's alpha
PIES_alpha <- psych::alpha(PIES_items)

############# ECM ##############
# select the relevant ECM items
## Continuance Intention
ECM_CI_items <- questionnaires %>%
  dplyr::select("ECM_CI1", "ECM_CI2", "ECM_CI3_rev")

## Satsifaction
ECM_S_items <- questionnaires %>%
  dplyr::select("ECM_S1", "ECM_S2", "ECM_S3", "ECM_S4")

## Perceived Usefulness
ECM_PU_items <- questionnaires %>%
  dplyr::select("ECM_PU1", "ECM_PU2", "ECM_PU3", "ECM_PU4")

# compute Cronbach's alpha 
ECM_CI_alpha <- psych::alpha(ECM_CI_items)

ECM_S_alpha <- psych::alpha(ECM_S_items)

ECM_PU_alpha <- psych::alpha(ECM_PU_items)

```

### Result NRQ

a. ECL

```{r}
#  NRQ ECL
print("Cronbach's alpha for NRQ ECL items:")
print(NRQ_ECL_alpha)
```

b. ICL

```{r}
# NRQ ICL
print("Cronbach's alpha for NRQ ICL items:")
print(NRQ_ICL_alpha)
```


### Result PIES

```{r}
# PIES
print("Cronbach's alpha for PIES items:")
print(PIES_alpha)
```

### Result ECM

a. Continuance Intention

```{r}
# Continuance Intention
print("Cronbach's alpha for ECM Continuance Intention items:")
print(ECM_CI_alpha)
```

b. Satisfaction

```{r}
# Satisfaction
print("Cronbach's alpha for ECM Satisfaction items:")
print(ECM_S_alpha)
```

c. Perceived Usefulness

```{r}
# Perceived Usefulness
print("Cronbach's alpha for ECM Perceived Usefulness items:")
print(ECM_PU_alpha)
```


# Manipulation Check

## Interest

### PIES

```{r}
# Linear Model (PIES ~ Interest)
mc_PIES <- lm(PIES_Score ~ interest * load, data = df)

# ANOVA
anova(mc_PIES)
#summary(mc_PIES)

# ANOVA table + partial eta^2 table
a <- anova(mc_PIES)

SS_error <- a["Residuals", "Sum Sq"]

effects <- setdiff(rownames(a), "Residuals")

out <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)

out


```
-> highly significant effect of interest on PIES: Successful interest manipulation

### ECM 

a. Continuance Intention

```{r}
# Linear Model (CI ~ Interest)
mc_ECM_CI <- lm(ECM_CI_Score ~ interest * load, data = df)

# ANOVA
anova(mc_ECM_CI)

# ANOVA table + partial eta^2 table
a <- anova(mc_ECM_CI)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

out_ECM_CI <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
out_ECM_CI
```

b. Satisfaction

```{r}
# Linear Model (S ~ Interest)
mc_ECM_S <- lm(ECM_S_Score ~ interest * load, data = df)

# ANOVA
anova(mc_ECM_S)

# ANOVA table + partial eta^2 table
a <- anova(mc_ECM_S)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

mc_ECM_S <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
mc_ECM_S
```

c. Perceived Usefulness

```{r}
# Linear Model (PU ~ Interest)
mc_ECM_PU <- lm(ECM_PU_Score ~ interest * load, data = df)

# ANOVA
anova(mc_ECM_PU)

# ANOVA table + partial eta^2 table
a <- anova(mc_ECM_PU)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

out_ECM_PU <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
out_ECM_PU
```
-> highly significant effect of interest on Continuance Intention, Satisfaction, and Perceived Usefulness 
-> good proxy for long-term utility


## Cognitive Load

### PAAS

```{r}
# Linear Model (PAAS ~ Load)
mc_PAAS <- lm(PAAS_Score ~ interest * load, data = df)

# ANOVA
anova(mc_PAAS)

# ANOVA table + partial eta^2 table
a <- anova(mc_PAAS)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

out_PAAS <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
out_PAAS
```
-> no significant effect of load on PAAS -> no effective manipulation

```{r}
# Check mean values of the PAAS Score by condition

## Mean PAAS Score by load
df %>%
  group_by(load) %>%
  summarise(n=n(),
            mean=mean(PAAS_Score, na.rm=TRUE),
            sd=sd(PAAS_Score, na.rm=TRUE))

## Mean PAAS Score by interest + load
df %>%
  group_by(load, interest) %>%
  summarise(n=n(),
            mean=mean(PAAS_Score, na.rm=TRUE),
            sd=sd(PAAS_Score, na.rm=TRUE),
            .groups="drop")

```

### NRQ

a. ICL

```{r}
# Linear Model (ICL ~ Load)
mc_NRQ_ICL <- lm(NRQ_ICL_Score ~ interest * load, data = df)

# ANOVA
anova(mc_NRQ_ICL)

# ANOVA table + partial eta^2 table
a <- anova(mc_NRQ_ICL)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

out_NRQ_ICL <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
out_NRQ_ICL
```

b. ECL

```{r}
# Linear Model (ECL ~ Load)
mc_NRQ_ECL <- lm(NRQ_ECL_Score ~ interest * load, data = df)

# ANOVA
anova(mc_NRQ_ECL)

# ANOVA table + partial eta^2 table
a <- anova(mc_NRQ_ECL)

SS_error <- a["Residuals", "Sum Sq"]
effects  <- setdiff(rownames(a), "Residuals")

out_NRQ_ECL <- data.frame(
  effect = effects,
  df1    = a[effects, "Df"],
  df2    = a["Residuals", "Df"],
  F      = a[effects, "F value"],
  p      = a[effects, "Pr(>F)"],
  eta_p2 = a[effects, "Sum Sq"] / (a[effects, "Sum Sq"] + SS_error)
)
out_NRQ_ECL
```

c. NRQ Total

```{r}
# # Linear Model (NRQ ~ Load)
mc_NRQ <- lm(NRQ_Score ~ interest * load, data = df)

# ANOVA
anova(mc_NRQ)
```
-> manipulation of cognitive load is not confirmed via self-report scales

### Further Investigation

```{r}
# Check mean values of the PAAS and NRQ ICL Score by load
df %>%
  group_by(load) %>%
  summarise(
    n = n(),
    mean_PAAS = mean(PAAS_Score, na.rm = TRUE),
    sd_PAAS   = sd(PAAS_Score, na.rm = TRUE),
    mean_ICL  = mean(NRQ_ICL_Score, na.rm = TRUE),
    sd_ICL    = sd(NRQ_ICL_Score, na.rm = TRUE),
    .groups="drop"
  )

```

- PAAS: almost no difference in means between the two groups (0.18)
- NRQ_ICL: almost no difference in means between the two groups (-0.10, also wrong direction)

Therefore, we are comparing Cohen's d

```{r}
# PAAS:
t_paas <- t.test(PAAS_Score ~ load, data = df)
cohens_d(PAAS_Score ~ load, data = df)

# ICL: High vs Low load
t_icl <- t.test(NRQ_ICL_Score ~ load, data = df)
cohens_d(NRQ_ICL_Score ~ load, data = df)

```
-> both estimates are close to zero which indicates that the average self-reported cognitive load is very similar across the two load conditions. This means, there is little evidence that participants experienced meaningfully different levels of cognitive load. In addition, the 95% confidence intervals include 0, which means that the data is also consistent with no true difference between conditions.



# Hypothesis Testing 

## HYPOTHESIS 1

### H1a

-> Interest in a product will increase the *mean velocity* of the cursor.

```{r}
# Linear Regression 1.1: Mean velocity
lm_H1a <- lm(log(mean_velocity_norm_s) ~ interest + load + log(trial_duration_s) + events_per_s + gender , data = df)
summary(lm_H1a)
```
-> No significant interest effect: H1a is not supported.

### H1b

-> Interest in a product will decrease the *total distance* traveled of the cursor.

```{r}
# Linear Regression 1.2: Total distance
lm_H1b <- lm(log(total_distance_norm) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H1b)
```
-> Significant interest effect: H1b is supported.

```{r}
# Calculate the change on the original scale
beta_distance <- (-0.17379)
beta_origin_distance <- exp(beta_distance)
pct_change_distance <- (beta_origin_distance - 1) * 100
pct_change_distance
```

-> Relative change of approx. -16%
-> Total cursor distance under high product interest is approximately 16% shorter than under low product interest

### H1c

-> Interest in a product will decrease the *number of submovements*.

```{r}
# Linear Regression 1.3: Submovements
lm_H1c <- lm(log(submovements) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H1c)
```

-> No significant interest effect: H1c is not supported.

### H1d

-> Interest in a product will decrease the *deviation from the straightest path* within a submovement.

```{r}
# Linear Regression 1.4: Deviation
lm_H1d <- lm(log(mean_submovement_deviation) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H1d)
```
-> No significant interest effect: H1d is not supported.


### H1e

-> Interest in a product will decrease the *total hover time*.

```{r}
# Linear Regression 1.5: Hover Time
lm_H1e <- lm(log(total_hovertime_s) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H1e)
```
-> Significant interest effect: H1e is supported.

```{r}
# Calculate change on the original scale
beta_hovertime <- (-0.22962)
beta_origin_hovertime <- exp(beta_hovertime)
pct_change_hovertime <- (beta_origin_hovertime - 1) * 100
pct_change_hovertime
```

-> Relative change of approx. -21%
-> Total hover time under high product interest is approximately 21% less than under low product interest


## HYPOTHESIS 2

```{r}
# Moderation Effect: Velocity
lm_H2a <- lm(log(mean_velocity_norm_s) ~ interest * load + log(trial_duration_s) + events_per_s + gender, data = df)   
summary(lm_H2a)
```

```{r}
# Moderation Effect: Distance
lm_H2b <- lm(log(total_distance_norm) ~ interest * load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H2b)
```

```{r}
# Moderation Effect: Submovements
lm_H2c <- lm(log(submovements) ~ interest * load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H2c)
```

d. SUBMOVEMENT DEVIATION

```{r}
# Moderation Effect: Submovement Deviation
lm_H2d <- lm(log(mean_submovement_deviation) ~ interest * load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H2d)
```

e. TOTAL HOVER TIME

```{r}
# Moderation Effect: Hover Time
lm_H2e <- lm(log(total_hovertime_s) ~ interest * load + log(trial_duration_s) + events_per_s + gender, data = df)
summary(lm_H2e)
```


-> The interaction term is not statistically significant for any of the five mouse metrics.
-> H2 is not supported.


# Further Exploratorive Analysis

## Direction Changes

### Descriptive Statistics

```{r}
# Descriptives
direction_changes_stats <- df %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    direction_changes_mean   = mean(n_direction_changes, na.rm = TRUE),
    direction_changes_sd     = sd(n_direction_changes, na.rm = TRUE),
    direction_changes_med    = median(n_direction_changes, na.rm = TRUE),
    direction_changes_iqr    = IQR(n_direction_changes, na.rm = TRUE),

    dir_changes_per_s_mean = mean(dir_changes_per_s, na.rm = TRUE),
    dir_changes_per_s_med  = median(dir_changes_per_s, na.rm = TRUE)
  )

direction_changes_stats
```

### Box Plot

```{r}
ggplot(df, aes(x = interest, y = dir_changes_per_s)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.25) +
  labs(x = "Interest", y = "Direction changes per second")
```

### Histogram

```{r}
# Histogram
hist(df$n_direction_changes,
     breaks = 30,
     main = "Distribution of direction changes",
     xlab = "Number of direction changes",
     ylab = "Count of participants")
```
-> right-skewed

### ANOVA

```{r}
# Define ANOVA function
anova_eta <- function(model) {
  a <- car::Anova(model, type = 2)
  SS_error <- a["Residuals", "Sum Sq"]
  effects  <- setdiff(rownames(a), "Residuals")
  
  data.frame(
    effect = effects,
    df1    = a[effects, "Df"],
    df2    = a["Residuals", "Df"],
    F      = a[effects, "F value"],
    p      = a[effects, "Pr(>F)"],
    eta_p2 = a[effects, "Sum Sq"] / 
             (a[effects, "Sum Sq"] + SS_error)
  )
}
```


```{r}
# Linear Model 1.1: Mean velocity
lm_Ex1 <- lm(log(1+n_direction_changes) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = df) # log(1+x) to handle zeros

## ANOVA
anova_eta(lm_Ex1)
```

-> No significant effect of direction changes

## Pause Analysis

### Descriptive Statistics

```{r}
# Descriptives
pause_stats <- pause_analysis %>%
  group_by(interest) %>%
  summarise(
    n = n(),
    pause_share_mean   = mean(pause_share, na.rm = TRUE),
    pause_share_sd     = sd(pause_share, na.rm = TRUE),
    pause_share_med    = median(pause_share, na.rm = TRUE),
    pause_share_iqr    = IQR(pause_share, na.rm = TRUE),

    total_pause_mean_s = mean(total_pause_time_s, na.rm = TRUE),
    total_pause_med_s  = median(total_pause_time_s, na.rm = TRUE),

    n_pauses_mean      = mean(n_pauses, na.rm = TRUE),
    n_pauses_med       = median(n_pauses, na.rm = TRUE),

    median_pause_med_s = median(median_pause_s, na.rm = TRUE),
    max_pause_med_s    = median(max_pause_s, na.rm = TRUE)
  )

pause_stats
```

### Boxplots

```{r}
# Boxplots
# Pause Share
ggplot(pause_analysis, aes(x = interest, y = pause_share)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.4) +
  labs(x = NULL, y = "Pause share",
       title = "Pause share by interest")

# Total Pause Time (s)
ggplot(pause_analysis, aes(x = interest, y = total_pause_time_s)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.4) +
  labs(x = NULL, y = "Total pause time (s)", title = "Total pause time by interest") 

# Number of Pauses
ggplot(pause_analysis, aes(x = interest, y = n_pauses)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, alpha = 0.4) +
  labs(x = NULL, y = "Number of pauses", title = "Number of pauses by interest")
```
### ANOVA 

a. Pause Share

```{r}
# Histogram
hist(pause_analysis$pause_share,
     breaks = 30,
     main = "Distribution of Pause Share",
     xlab = "Pause Share",
     ylab = "Count of participants")
```
-> not skewed 

```{r}
# Linear Model: Pause share ~ interest
lm_Ex2 <- lm(pause_share ~ interest + load + events_per_s + gender, data = pause_analysis) # no control for trial duration because it is part of pause share

## ANOVA
anova_eta(lm_Ex2)
```
-> Significant effect of interest on pause share.


b. Number of Pauses

```{r}
# Histogram
hist(pause_analysis$n_pauses,
     breaks = 30,
     main = "Distribution of Number of Pauses",
     xlab = "Number of Pauses",
     ylab = "Count of participants")
```

-> right-skewed -> log-transformation

```{r}
# Linear Model: Number of Pauses
lm_Ex3 <- lm(log(n_pauses) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = pause_analysis) 

## ANOVA
anova_eta(lm_Ex3)
```
-> No significant effect of interest on the number of pauses.


c. Total Pause Time

```{r}
# Histogram
hist(pause_analysis$total_pause_time_s,
     breaks = 30,
     main = "Distribution of Total Pause Time",
     xlab = "Total Pause Time (s)",
     ylab = "Count of participants")
```
-> right-skewed -> log-transformation

```{r}
# Linear Model: Total Pause Time
lm_Ex4 <- lm(log(total_pause_time_s) ~ interest + load + log(trial_duration_s) + events_per_s + gender, data = pause_analysis) 

## ANOVA
anova_eta(lm_Ex4)
```
-> Significant effect of interest on total pause time. 



-> Result: Participants in the high interest group have a statistically significant greater pause share and total pause time than in the low interest group. In contrast, the number of pauses is not statistically significant between the two interest groups. This means, under high interest, pauses are significantly longer but not more frequently.


## Velocity Time Analysis 

### Descriptive Statistics

```{r}
# Velocity by phase and interest
phase_statistics <- velocity_by_phase %>%
  group_by(interest, phase) %>%
  summarise(
    n = n(),
    mean_velocity = mean(mean_velocity_norm_s, na.rm = TRUE),
    sd_velocity   = sd(mean_velocity_norm_s, na.rm = TRUE),
    mean_total_distance = mean(total_distance_norm, na.rm = TRUE),
    sd_total_distance   = sd(total_distance_norm, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(interest, phase)

phase_statistics

```

### Box Plot

```{r}
# Boxplot (Mean Velocity by Interest x Phase)
ggplot(velocity_by_phase, aes(x = phase, y = mean_velocity_norm_s, fill = interest)) +
  geom_boxplot(position = position_dodge(width = 0.8), outlier.alpha = 0.4) +
  labs(
    x = "Phase",
    y = "Mean velocity (norm/s)",
    fill = "Interest"
  ) +
  theme_minimal()

ggplot(velocity_by_phase, aes(x = phase, y = mean_velocity_norm_s, fill = interest)) +
  geom_boxplot(position = position_dodge(width = 0.8), outlier.alpha = 0.2) +
  geom_jitter(aes(color = interest),
              position = position_jitterdodge(jitter.width = 0.15, dodge.width = 0.8),
              alpha = 0.35, size = 1.2) +
  labs(x = "Phase", y = "Mean velocity (norm/s)", fill = "Interest", color = "Interest") +
  theme_minimal()
```

### ANOVA

a. Early Phase

```{r}
# Linear Model: Early Phase
lm_early <- lm(log(1+mean_velocity_norm_s) ~ interest + load + log(trial_duration_s),
               data = velocity_by_phase %>% filter(phase == "early"))

# ANOVA
anova_eta(lm_early)
```
-> Significant interest effect in the early phase


b. Middle Phase

```{r}
# Linear Model: Mid Phase
lm_mid   <- lm(log(1+mean_velocity_norm_s) ~ interest + load + log(trial_duration_s),
               data = velocity_by_phase %>% filter(phase == "mid"))

# ANOVA
anova_eta(lm_mid)
```
-> No significant interest effect in the mid phase

c. Late Phase

```{r}
# Linear Model: Late Phase
lm_late  <- lm(log(1+mean_velocity_norm_s) ~ interest + load + log(trial_duration_s),
               data = velocity_by_phase %>% filter(phase == "late"))

# ANOVA
anova_eta(lm_late)
```
-> No significant interest effect in the late phase



